Time stability in human interaction networks (Supporting Information)

### 2015-06-22 supportingInformation.tex
detalhe de texto
pequenos retoques de escrita

\title[Interaction networks stability, Supporting Information]{Time stability in human interaction networks, Supporting Information}% Force line breaks with \\

@@

This document presents supporting information for the article describing interaction networks stability~\cite{tpaper}.
Section~\ref{sec:time} exhibits activity statistics in time (circular statistics and histograms) and among participants;
Section~\ref{si:frac} exposes the fraction of vertices in the peripheral, intermediary and hub sectors;
Section~\ref{si:pcat} exemplifies the combination of basic topological measures into principal components with greater variance;
There is a focus on email list interaction networks for benchmarking and
Section~\ref{si:ext} reinforces the results with the analysis of networks from Facebook, Twitter and Participa.br.
The interested reader should follow Section~\ref{scripts} of the main article~\cite{tpaper} to access both data and routines.

>>>>

\title[Interaction networks stability (Supporting Information)]{Time stability in human interaction networks (Supporting Information)}% Force line breaks with \\

@@

The supporting information (this document) contains statistics for time activity (circular statistics and histograms) in Section~\ref{sec:time}, the fraction of vertices in the peripheral, intermediary and hub sectors in Section~\ref{si:frac} and the combination of basic topological measures into principal components with greater variance in Section~\ref{si:pcat}. There is a focus on email list interaction networks for benchmarking and
Section~\ref{si:ext} reinforces the results with the analysis of networks from Facebook, Twitter and Participa.br.
More context (e.g. methods, discussion, data and scripts) is given in the main document~\cite{tpaper}.
